MSDS6372Project1

### 2021-02-02 MSDS6372Project1.Rmd
update test RMSE for regression tree

#####################################################
# Compare Forward vs. Backward on Test set to LASSO #
#####################################################
# Test result
test.result = test$MSRP
# str(test)
test = test[,-15] #delete MSRP for prediction
#Forward test results
forward.pred = predict(forward.regression,test)
# See forward test ASE
testMSE_Forward<-mean((test.result-forward.pred)^2)
testMSE_Forward #46054176

#Backward test results
backward.pred = predict(backward.regression,test)
# See backward test ASE
testMSE_Backward<-mean((test.result-backward.pred)^2)
testMSE_Backward #44935730

#LASSO test result
lasso.pred2 = predict(lasso.lm,test)
# See LASSO test ASE after refit
testASE_LASSO_2 = mean((test.result-lasso.pred2)^2)
testASE_LASSO_2 #35982124

@@

# seems k=2 gives the best result according to our test ASE
fit = knnreg(trainX,trainY,k=2)
plot(testY,predict(fit,testX))
#Try testing testASE
knn.k2.pred = predict(fit,testX)
testASE_KNN_k2 = mean((testY-knn.k2.pred)^2)
sqrt(testASE_KNN_k2)

>>>>

#####################################################
# Compare Forward vs. Backward on Test set to LASSO #
#####################################################
# Test result
test.result = test$MSRP
# str(test)
test = test[,-15] #delete MSRP for prediction
#Forward test results
forward.pred = predict(forward.regression,test)
# See forward test ASE
testMSE_Forward<-mean((test.result-forward.pred)^2)
sqrt(testMSE_Forward) #test RMSE = 6786.323

#Backward test results
backward.pred = predict(backward.regression,test)
# See backward test ASE
testMSE_Backward<-mean((test.result-backward.pred)^2)
sqrt(testMSE_Backward) #test RMSE = 6702.666

#LASSO test result
lasso.pred2 = predict(lasso.lm,test)
# See LASSO test ASE after refit
testASE_LASSO_2 = mean((test.result-lasso.pred2)^2)
sqrt(testASE_LASSO_2) #test RMSE = 5998.51

@@

# seems k=2 gives the best result according to our test ASE
fit = knnreg(trainX,trainY,k=2)
plot(testY,predict(fit,testX))
#Try testing testASE
knn.k2.pred = predict(fit,testX)
testASE_KNN_k2 = mean((testY-knn.k2.pred)^2)
sqrt(testASE_KNN_k2) # test RMSE = 6861.357
